Sparse Function-space Representation \\ of Neural Networks

### 2023-05-23 paper/main.tex
fixed small typo
Add accuracy table, stash template to uci_all_example.tex

\par All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching. In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} for the complete results. Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.

@@

@@

%% Placeholders for now
\textbf{S-FMNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate $1 \cdot 10^{-3}$, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1.0$, $\delta=0.0001$, number of epochs=5.
\end{itemize}

>>>>

\par All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching. In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendic-acc} for the complete NLPD and accuracy results. Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{The accuracy of our \our method compared to a GP subset based method which discards most of the data. Even with a small $M$ our method is able to provide good results.} 
	\label{tbl:uci-appendix-acc}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.25\textwidth}

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/uci_all_acc.tex}
\end{table}

@@

%% Placeholders for now
\textbf{S-FMNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate $1 \cdot 10^{-3}$, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha =  0.2$, reservoir buffer size 200.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1.0$, $\delta=0.0001$, number of epochs=5.
\end{itemize}
